Probing heavy ion collisions using quark and gluon jet substructure

### 2020-02-25 qg_ML.tex
updated figure17 with the embedding curve with DCNN and text

\begin{figure}[h]
	\centering
        \includegraphics[width=0.8\textwidth]{Fig17}
	\caption{ROC curves of quark v.s. gluon efficiency highlighting the effect of the embedded \textsc{Hydjet} background. The dashed curves represent the embedded event in comparison to the solid curves which show the vacuum events. The different colored curves correspond to various classification models studied in this paper.}
	\label{fig:ROC_qvsg_wHydjet}
\end{figure}

The fluctuating underlying event and their subtraction in experiment can both influence and introduce features in jet substructure. We employ the embedding technique which is used in almost all experiments to estimate the effect of these fluctuations on a event by event basis. We take an unbiased heavy ion event produced by the \textsc{Hydjet}~\cite{Lokhtin:2008xi} MC for most central collisions ($0-5\%$) and embed the particles produced by \jw (both vacuum and in-medium) together. In this embedded event, we have included the effect of the uncorrelated background to jets. Since the \jw events with jet quenching are for a centrality window of $0-20\%$, this underlying event presents an over estimate of the background which we take as an upper bound for the effects due to the underlying event. In order to extract jets from these embedded events, we perform constituent subtraction~\cite{Berta:2014eza} which reduces the contribution of the background to the jet and its constituents. The effect of including the heavy ion underlying event is shown in Figure~\ref{fig:ROC_qvsg_wHydjet} in the dashed curves having an overall reduction in classification performance as shown by a reduced auc for both vacuum jets and quenched jets but we would like to note that classification is still experimentally viable albeit with reduced efficiency. Further studies of the exact nature of the background influence on jet substructure via detector simulations are reserved for future publications.

>>>>

\begin{figure}[h]
	\centering
        \includegraphics[width=0.8\textwidth]{Fig17}
	\caption{ROC curves of quark v.s. gluon efficiency with the DCNN method highlighting the effect of the embedded \textsc{Hydjet} background shown in the red curves in comparison to the blue curves which are in vacuum at the generator level. The solid and dotted  curves correspond to PbPb quenched and pp events respectively.}
	\label{fig:ROC_qvsg_wHydjet}
\end{figure}

The fluctuating underlying event and their subtraction in experiment can both influence and introduce features in jet substructure. We employ the embedding technique which is used in almost all experiments to estimate the effect of these fluctuations on an event by event basis. We take an unbiased heavy ion event produced by the \textsc{Hydjet}~\cite{Lokhtin:2008xi} MC for most central collisions ($0-5\%$) and embed the particles produced by \jw (both vacuum and in-medium) together. In this embedded event, we have included the effect of the uncorrelated background to jets. Since the \jw events with jet quenching are for a centrality window of $0-20\%$, this underlying event presents an over estimate of the background which we take as an upper bound for the effects due to the underlying event. In order to extract jets from these embedded events, we perform constituent subtraction~\cite{Berta:2014eza} which reduces the contribution of the background to the jet and its constituents. The effect of including the heavy ion underlying event is shown in Figure~\ref{fig:ROC_qvsg_wHydjet} in the dashed curves having an overall reduction in DCNN classification performance as shown by an increased auc for both vacuum jets and quenched jets but we would like to note that classification is still experimentally viable albeit with reduced efficiency. We test the DCNN method for this embedding study since it is agnostic to jet substructure artifacts introduced during the embedding and background subtraction procedures. Further studies of the exact nature of the background influence on jet substructure via detector simulations are reserved for future publications.
